A fast global code motion algorithm for code size optimization

### 2017-10-29 paper.tex
added explanation for chi

%% Title information
\title[SSA GCM]{Global code motion of congruent instructions}         %% [Short Title] is optional;
                                        %% when present, will be used in
                                        %% header instead of Full Title.
%\titlenote{with title note}             %% \titlenote is optional;
                                        %% can be repeated if necessary;
                                        %% contents suppressed with 'anonymous'
%\subtitle{Subtitle}                     %% \subtitle is optional
%\subtitlenote{with subtitle note}       %% \subtitlenote is optional;
                                        %% can be repeated if necessary;
                                        %% contents suppressed with 'anonymous'

@@

% TODO: References
% Sink instructions
% Ranking of instructions from Zadeck
% Liveness analysis from Ramakrishna
% Experimental results: Register spills, compile time, run time.

>>>>

%% Title information
\title[SSA GCM]{A fast global code motion algorithm for code size optimization}         %% [Short Title] is optional;
                                        %% when present, will be used in
                                        %% header instead of Full Title.
%\titlenote{with title note}             %% \titlenote is optional;
                                        %% can be repeated if necessary;
                                        %% contents suppressed with 'anonymous'
%\subtitle{Subtitle}                     %% \subtitle is optional
%\subtitlenote{with subtitle note}       %% \subtitlenote is optional;
                                        %% can be repeated if necessary;
                                        %% contents suppressed with 'anonymous'

@@

% TODO: References
% Sink instructions
% Ranking of instructions from Zadeck
% Liveness analysis from Ramakrishna
% Experimental results: Register spills, compile time, run time.
\section{Code hoisting of congruent computations}
Examples to show CHI insertion.

The algorithm factors out the reachability of values such that multiple queries
to find reachability of values are fast. This is based on finding the ANTIC
points in the CFG which do not change during hoisting. The ANTIC points are
basically the dominance-frontiers in the inverse graph. So we introduce a data
structure (CHI nodes) to keep track of values flowing out of a basic block. We
only do this for values with multiple occurrences in the function as they are
the potentially hoistable candidates. This approach allows us to hoist
instructions to a basic block with more than two successors, as well as deal
with infinite loops in a trivial way.

Limitations: This pass does not hoist fully redundant expressions because they
are already handled by GVN-PRE. It is advisable to run gvn-hoist before and
after gvn-pre because gvn-pre creates opportunities for more instructions to be
hoisted.

\includegraphics[width=0.8\textwidth,height=8cm]{chi-example.pdf}

A CHI keeps information about values flowing out of a basic block.  It is
similar to PHI but in the inverse graph, and used for outgoing values on each
edge. For conciseness, it is computed only for instructions with multiple
occurrences in the CFG because they are the only hoistable candidates.

The global value number for both I1 and I2 is V, the CHI node will save the
instruction as well as the edge where the value is flowing to.  Where CHIArg1,
CHIArg2 are of type CHIArg.

\begin{verbatim}
struct CHIArg {
  // Edge destination (shows the direction of flow), may not be where the I is.
  BasicBlock *Dest;
  // The instruction which uses the values flowing out of CHI.
  Instruction *I;
  // The global value number of I.
  GVNType VN;
};

\end{verbatim}

Essentially, CHIArg1 = {V, B, I1} and CHIArg2 = {V, C, I2}

For sinking we use the similar approach as \ref{SSAPRE} to track values flowing
into a basic block.

TODO: Explain ranking
